Pre-registered Analyses

### 2020-05-28 pre-registered_analyses.Rmd
bonferroni corrections applied

```{r H2, include=TRUE}
# create new variable for atypicality 
LIs <- 
  LIs %>% 
  mutate(atypicality= ifelse(Day1_CF_acc_Z > 1.96 & Day1_Dich_acc_Z < -1.96, "typical",
                          ifelse(Day1_CF_acc_Z > 1.96 & Day1_Dich_acc_Z > 1.96, "atypical dichotic",
                                 ifelse(Day1_CF_acc_Z < -1.96 & Day1_Dich_acc_Z < -1.96, "atypical face",
                                        ifelse(Day1_CF_acc_Z < -1.96 & Day1_Dich_acc_Z > 1.96, "atypical both", NA)))))
# create handedness for handedness on EHI 
LIs <- 
  LIs %>% 
  mutate(hand_90= ifelse(index_EHI >= 90, "right handed",
                         ifelse(index_EHI <= -9, "left handed", NA)))
# create a table for chi-squared
tbl <- table(LIs$atypicality, LIs$hand_90)
tbl
# run chi squared
chisq.test(tbl)
# use balloon plot to visualise
gplots::balloonplot(t(tbl), main ="Association of EHI handeness and atypical laterality", xlab ="", ylab="",
            label = FALSE, show.margins = FALSE)
```

>>>>

**Rhyme**

```{r H2 dichotic, include=TRUE}
# create new variable for atypicality 
LIs <- 
  LIs %>% 
  mutate(atypicality_rhyme= ifelse(Day1_CF_acc_Z > 1 & t1 < -1, "typical",
                          ifelse(Day1_CF_acc_Z > 1 & t1 > 1, "atypical rhyme",
                                 ifelse(Day1_CF_acc_Z < -1 & t1 < -1, "atypical face",
                                        ifelse(Day1_CF_acc_Z < -1 & t1 > 1, "atypical both", NA)))))
# create handedness for handedness on EHI 
LIs <- 
  LIs %>% 
  mutate(hand_90= ifelse(index_EHI >= 90, "right handed",
                         ifelse(index_EHI <= -9, "left handed", NA)))
# create a table for chi-squared
tbl <- table(LIs$atypicality_rhyme, LIs$hand_90)
tbl
# run chi squared
chisq.test(tbl)
p <- chisq.test(tbl)[3]
p.adjust(p, "bonferroni", n=2)
# use balloon plot to visualise
gplots::balloonplot(t(tbl), main ="Association of EHI handeness and atypical laterality (faces and rhyme)", xlab ="", ylab="",
            label = FALSE, show.margins = FALSE)
```

With the rhyme task, the reliability is low. Because of this we have to use a t value that is less than 1.96 (i.e. larger than 0.05). This produces no association. But, this isn't a big deal as we can't be sure that the task is measuring language lateralisation.

**Dichotic**

```{r H2 dichotic, include=TRUE}
# create new variable for atypicality 
LIs <- 
  LIs %>% 
  mutate(atypicality_dichotic= ifelse(Day1_CF_acc_Z > 1.96 & Day1_Dich_acc_Z < -1.96, "typical",
                          ifelse(Day1_CF_acc_Z > 1.96 & Day1_Dich_acc_Z > 1.96, "atypical dichotic",
                                 ifelse(Day1_CF_acc_Z < -1.96 & Day1_Dich_acc_Z < -1.96, "atypical face",
                                        ifelse(Day1_CF_acc_Z < -1.96 & Day1_Dich_acc_Z > 1.96, "atypical both", NA)))))
# create handedness for handedness on EHI 
LIs <- 
  LIs %>% 
  mutate(hand_90= ifelse(index_EHI >= 90, "right handed",
                         ifelse(index_EHI <= -9, "left handed", NA)))
# create a table for chi-squared
tbl <- table(LIs$atypicality_dichotic, LIs$hand_90)
tbl
# run chi squared
chisq.test(tbl)
p <- chisq.test(tbl)[3]
p.adjust(p, "bonferroni", n=2)
# use balloon plot to visualise
gplots::balloonplot(t(tbl), main ="Association of EHI handeness and atypical laterality (faces and dichotic)", xlab ="", ylab="",
            label = FALSE, show.margins = FALSE)
```
